Project assignment - Tahoe-LAFS with SHA-3 candidates

### 2010-11-13 paper/main.tex
Semi-done selection of SHA-3 implementation

\begin{acronym}
\acro{AES}{Advanced Encryption Standard}
\acro{API}{Application programming interface}
\acro{CEB}{Capability Extension Block}
\acro{FEC}{Forward Error Correction}
\acro{LAFS}{Least-Authority Filesystem}
\acro{NIST}{National Institute of Standards and Technology}
\acro{RAM}{Random Access Memory}
\acro{RAID}{Redundant Array of Independent Disks}
\acro{SHA}{Secure Hash Algorithm}
\acro{SSE2}{Streaming SIMD Extensions 2}
\acro{SSSE3}{Supplemental Streaming SIMD Extensions 3}
\acro{SUPERCOP}{System for Unified Performance Evaluation Related to
Cryptographic Operations and Primitives}
\acro{UEB}{URI Extension Block}
\end{acronym}

@@

\section{Choosing implementations of the SHA-3 Candidates}

>>>>

\begin{acronym}
\acro{AES}{Advanced Encryption Standard}
\acro{API}{Application programming interface}
\acro{CEB}{Capability Extension Block}
\acro{FEC}{Forward Error Correction}
\acro{KAT}{Known Answer Test}
\acro{LAFS}{Least-Authority Filesystem}
\acro{NIST}{National Institute of Standards and Technology}
\acro{RAM}{Random Access Memory}
\acro{RAID}{Redundant Array of Independent Disks}
\acro{SHA}{Secure Hash Algorithm}
\acro{SSE2}{Streaming SIMD Extensions 2}
\acro{SSSE3}{Supplemental Streaming SIMD Extensions 3}
\acro{SUPERCOP}{System for Unified Performance Evaluation Related to
Cryptographic Operations and Primitives}
\acro{UEB}{URI Extension Block}
\end{acronym}

@@

\section{Choosing implementations of the SHA-3 Candidates}
While the official \ac{NIST} \ac{SHA}-3 second round submissions contains both
reference and different optimized version of the candidates does not appear to
be updateded since the submission deadline on September 15, 2009. They also do
not contain any benchmarking util which could be used to decide on the best
implementation for a particular plattform or architecture. \ac{SUPERCOP} on the
other hand provides both, in combination with results stating which compiler
arguments gives the best performance. On the downside the \ac{SUPERCOP}
\ac{API} only specifies the crypto\_hash() function and not an Update()
function which Tahoe-\ac{LAFS} is dependant on.

Since Tahoe-\ac{LAFS} uses \ac{SHA}-256 internally, we use only \ac{SHA}-3
functions with 256-bit output in our implementation. The results of \ac{SHA}-3
256-bit functions and \ac{SHA}-256 benchmarking in \ac{SUPERCOP} can be seen in
tables... % FIXME

We then chose the fastest implementation of each candidate that conforms to the
following criterias.
\begin{enumerate}
    \item The implementation must have an \ac{API} defined in C. (Not only
    assembly)
    \item The implementation must include a working Update() function.
    \item The implementation must not use assembly which can not be made
    position independant by gcc.
    \item The implementation should conform to the \ac{KAT}s specified in the
    \ac{NIST} submission package, or later updates by the author
\end{enumerate}
